Supplementary materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-24 analysis/paper/supplementary_materials.Rmd
Add effect size objects for reporting in supplementary tables

## Supplementary Figures

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability. Scoring for 'Code Availability' was scored 0--3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
y_labs <- gsub("abbreviation", "", parameters(m_f1)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:22, 1:20)]

p <- plot(equivalence_test(m_f1)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
))
```

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles’ supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
y_labs <- gsub("abbreviation", "", parameters(m_f2)$Parameter)
y_labs <- rev(gsub("b_", "", y_labs))
y_labs <- y_labs[c(21:23, 1:20)]

p <- plot(equivalence_test(m_f2)) +
  scale_y_discrete(labels = y_labs)

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
))
```

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
p <- plot(equivalence_test(m_g1))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
))
```

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability. Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
p <- plot(equivalence_test(m_g2))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
))
```

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability. Scoring for 'Code Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable."}
p <- plot(equivalence_test(m_h1))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
))
```

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability.  Scoring for 'Data Availability' was a 0--3 scale described as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
p <- plot(equivalence_test(m_h2))

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
))
```

>>>>

## Supplementary Figure

@@
